```{r ,echo=FALSE}
today <- Sys.Date()
today<- format(today, format="%B %d %Y")
```

---
title: "Coursera-JHU: Developing Data Products, Week2-Assignment"
author: 'Shovit Bhari'
date: `r today`
always_allow_html: yes
---

### Southern California Mountains Hiked During Summer 2019

As a part of Week 2 assignment, I created a map of all the Southern California mountains that my colleague Ionel and I hiked during the Summer of 2019. We were destined to be on the top of Mt. Whitney (elevation 14,505 feet) on August 3rd. Mt. Whitney is the higest mountain in the contiguous United States and falls on the popular Sierra Nevada range. To train and condition our body we hiked four other mountains greater than 10,000 feet in Southern California during the months of June and July.


#### Instructions
There are five markers tagged in the map below. When you click on the markers, it will display the name of the peak and it's elevation. 

```{r}
library(leaflet)
peaks <- c("Mt.Whitney", "Mt. San Gorgonio", "Mt. San Jacianto", "San Bernardino Peak", "Mt. San Antonio (aka Baldy)")
elevation <- c(14505, 11503, 10833, 10649, 10069)
pe <- paste(peaks,",", elevation, "feet")

socalLongLat <- data.frame(
        lat = c(36.5784973, 34.0995742, 33.8144612, 34.1244534, 34.2646853),
        lng = c(-118.3097696, -116.8334641, -116.696693, -116.9119811,  -117.722961 ))

socalLongLat %>%
        leaflet() %>%
        addTiles() %>%
        addMarkers(popup=pe)

```






